### 2019-07-19 manuscript.tex
Update manuscript.tex

In most part of the world, FGC is defined as violating human rights \cite{WHO97, WHO08} \cfonly{add and update}.  The commonly shared position of FGC is about to abolish than to intervene the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.  Yet, the progress of intervention is hindered due to the complicated history \cite{BergDeni12, Cami16}.  FGC is embodied with multiple meanings with cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}. \cfonly{too many cites}.  Understanding values and meanings attached to FGC is essential to comprehend the persistence of FGC practice \cite{}.  Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, is a key approach in fathoming the behaviour for intervention \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.

Identifying FGC norm is crucial in intervention of sustainable changes \cite{EffeVogt15, RimaLapi15} \cfonly{Bicc etc, more}.  Convention theory, a widely \jdcmt{not sure what this word means; inferred} approach in FGC research, posits that FGC is an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group coordination, \jd{s. starting to run on} and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.  FGC is also viewed as social capital for inclusion within women’s social groups \cite{Shel-Wand11}.  When the norms within the communities are strong, individuals tend to self-enforce community norms \jdcmt{this seems circular; self-enforcing is the definition of norms} \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be interdependent and interconnected across generations  \cite{Mack00, DuncWand11, ShelWand11}. \cfonly{add \cite{Bicc15}}.

Although convention theory was \jdcmt{doesn't seem to mean anything; well deliberated and applied} and showed a \jdcmt{larger (than what?  do you just mean large?)} effect on FGC practices (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), it was not without challenges and no coordination game was observed in marital expectation \cite{EffeVogt15} \jdcmt{By anyone? Or just by them? It is hard for the reader to reconcile this statement with the previous one}.  Studies show that there may be more than one \jdcmt{you seem to be conflating determining factors with tipping points; tipping point} other than marriageability \jdcmt{more than one total? or more than one other? this is awkward} underlying women’s fgc decisions \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?} \jdcmt{run-on and hard to parse:} as well as that it can be a social bond for women \cite{Mack00, DuncWand11}.  Multiple theoretical frameworks were \jdcmt{what does this mean; called to be incorporated to grasp a full explanation} of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13} \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, PashPonn16, ShelHern06,}}

In this study, we consider multiple social determinants of FGC practice both at a individual and a community level to analyze how community of FGC expectation and beliefs associates with individual attitudes on the practice.  In addition to \jdcmt{hard to figure out what this means in this context, do you just mean attitudes about FGC? social norms of FGC,} we also incorporated information about women’s gender values and their \jdcmt{Can you explain this? social environment.}

@@

- conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} vs. 
- \cite{PashPonn16}:  “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." also their findings showed that beliefs of fgc benits was the strongest predictor of mother’ intention of cutting daughters.
\cite{ShelWand11}:“alternative convention/peer convention.  Subjective norm referred to “perceived social pressure to perform or not to perform the behavior” or “socially expected mode of conduct”  \cite{Ajze91}.

>>>>

In most part of the world, FGC is defined as violating human rights \cite{WHO97, WHO08} \cfonly{add and update}.  The commonly shared position of FGC is about to abolish than to intervene the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.  Yet, the progress of intervention is hindered due to the complicated history \cite{BergDeni12, Cami16}.  FGC is embodied with multiple meanings with cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}. \cfonly{too many cites}.  Understanding values and meanings attached to FGC is essential to comprehend the persistence of FGC practice \cite{}.  Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, is is crucial in intervention of sustainable changes \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.

Convention theory, a widely regarded approach in FGC norm research, posited first that FGC was a marriageability convention and, latter on, a social norm and others, such as religious obligation, adolescent rite of passage, and female honour and modesty as an important norm to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08}.  The convention theory views FGC as a social behaviour resulting from group coordination \cite{Mack00, MackLeJe08}.  FGC was also viewed as a social capital, a value expected by women for inclusion within women’s social groups \cite{ShelWand11}. Basically, when the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be interdependent and interconnected across generations  \cite{Mack00, ShelWand11}. \cfonly{add \cite{Bicc15}}.  Although normative behaviour based on convention theory was well documented regarding analysis of persistence of FGC practices (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), it was not without challenges \cite{EffeVogt15, Njam04}.  For example, there was no coordination game observed in marital expectation \cite{EffeVogt15}.  it was also argued that anti-FGC discourse perpetuated a colonial assumption by universalizing a western view of normal body and sexuality \cite{Njam04}.  Studies showed that factors other than marriageability have underlined women’s fgc decisions \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.

Multiple theoretical frameworks were \jdcmt{what does this mean; called to be incorporated to grasp a full explanation} of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13} \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, PashPonn16, ShelHern06,}}  In this study, we consider multiple social determinants of FGC practice both at a individual and a community level to analyze how community of FGC expectation and beliefs associates with individual attitudes on the practice.  In addition to \jdcmt{hard to figure out what this means in this context, do you just mean attitudes about FGC? social norms of FGC,} we also incorporated information about women’s gender values and their \jdcmt{Can you explain this? social environment.}

@@

- conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} vs. 
- \cite{PashPonn16}:  “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." also their findings showed that beliefs of fgc benits was the strongest predictor of mother’ intention of cutting daughters.
\cite{ShelWand11}:“alternative convention/peer convention.  Subjective norm referred to “perceived social pressure to perform or not to perform the behavior” or “socially expected mode of conduct”  \cite{Ajze91}. 
% come back to the concept of self-enforce community norms mentioned in the introduction.  As jd agreed, this is a crucial concept linking to our findings.
